Cluster Difference Imaging Photometric Survey. I. Light Curves of Stars in Open Clusters from TESS Sectors 6 \& 7

### 2019-08-12 paper_I/ms.tex
paper: update figures. minor tweaks.

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{target_star_positions.png}
		%\gridline{\fig{target_star_cumulative_counts.pdf}{0.41\textwidth}{}}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    Target star positions (blue) and nominal TESS observing footprint
    (gray).  Target stars are either candidate members of clusters, or
    else have other youth indicators (see \S~\ref{sec:starselection}).
    Most will be observed for one or two lunar months during the TESS
    Prime Mission.  Camera 1 is centered at $(l,b)=(203^\circ,
    -6^\circ)$ and $(218^\circ,15^\circ)$ in Sectors 6 and 7,
    respectively.
    \label{fig:cdips_targets_positions}
	}
\end{figure*}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		%\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
		\gridline{\fig{target_star_cumulative_counts.pdf}{0.43\textwidth}{}}
		\vspace{-0.8cm}
		\gridline{\fig{target_star_hist_logt.pdf}{0.43\textwidth}{}}
		\vspace{-0.8cm}
		\gridline{\fig{target_star_reference_pie_chart.pdf}{0.43\textwidth}{}}
	\end{center}
	\vspace{-0.8cm}
	\caption{
		Target star statistics.
		{\it Top.} Cumulative counts as a function of Gaia $Rp$-band
		magnitude.  
		{\it Middle.} Histogram of target star ages, for the subset of
		stars with ages matched against \citet{Kharchenko_et_al_2013}.
		{\it Bottom.} Provenance of cluster membership.  Percentages are
		relative to $N_{\rm total}=1{,}061{,}446$ target stars. Symbols
		are as follows.
		D14 is \citet{dias_proper_2014}.
		K13 is \citet{Kharchenko_et_al_2013}.
		CG18 is \citet{cantat-gaudin_gaia_2018}.
		Z18 is \citet{zari_3d_2018}, with upper main sequence and
		pre-main-sequence samples sub-divided.
		``$\geq 2$'' indicates at least two authors reported a star as a
		candidate cluster member.
		%``Other'' refers to sources enumerated in \S~\ref{sec:starselection}.
		\label{fig:cdips_targets}
	}
\end{figure}

@@

\citet{Kharchenko_et_al_2013} used proper motions calculated in PPMXL
\citep[][a combination of USNO-B1{.}0 and 2MASS
astrometry]{roeser_ppmxl_2010} and near-infrared photometry from 2MASS
\citep{skrutskie_tmass_2006} to report the existence of 2859 open
clusters and stellar associations (globular clusters were omitted by
excluding any entry of type \texttt{'g'}).  We selected the most
probable cluster members (``$1\sigma$ members'') using the combined
photometric, kinematic, and spatial criteria described by
\citet[][Section~3.3]{kharchenko_global_2012}.  Then, to obtain {\it
Gaia}-DR2 source identifiers for the members, we performed a
crossmatch for Gaia-DR2 sources within 5 arcseconds of the listed
positions.  To improve the quality of the cross-match, we used the
2MASS photometry to predict the $G$-band magnitudes\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GDR2/Data_processing/chap_cu5pho/sec_cu5pho_calibr/ssec_cu5pho_PhotTransf.html},
online, \texttt{2019-03-29}, or \citet{carrasco_gaia_2016}}, and
required that the measured $G$-magnitude fall within 2 magnitudes of
the predicted $G$-magnitude.  If multiple neighbors matched the
position and magnitude constraints, we took the nearest spatial
neighbor as the match.  From 373{,}226 stars, this yielded a unique
best neighbor for 352{,}332 stars (94.4\% of the sample), and a choice
between two neighbors for 17{,}774 stars.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.25\textwidth]{pipelineoverview.pdf}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    Conceptual overview of photometric reduction pipeline.
    Details are given in \S~\ref{sec:method}.
	\label{fig:pipeline}
	}
\end{figure}

\begin{figure*}[!t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.93\textwidth]{stages_of_image_processing_good.png}
    \end{center}
    \vspace{-0.6cm}
    \caption{
        Stages of image processing for an image obtained during the middle
        of an orbit.
        {\it Top right}. Calibrated image.
        {\it Top left}. Smooth background estimate.
        {\it Middle right}. Calibrated image minus its median pixel value.
        {\it Middle left}. Calibrated image minus smooth background.
        {\it Bottom left}. Registered difference image.
        {\it Bottom right}. Zoom of difference image.
        Each image is $(2048\times2048)$ pixels, except for the
        bottom-right image, which is $(500\times500)$.  All images
        except the top-right have the same color map.  The sector,
        camera, and CCD are (6, 1, 2).
        \label{fig:stages_good}
    }
\end{figure*}

\begin{figure*}[!t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.93\textwidth]{stages_of_image_processing_bad.png}
    \end{center}
    \vspace{-0.6cm}
    \caption{
        Same sector, camera and CCD as Figure~\ref{fig:stages_good},
        but for an image obtained during perigee passage, when
        scattered light from the Earth is prominent.  A number of
        systematic artifacts are present, including vertical
        ``straps'' and small-scale structure in scattered light
        patches.  The quality of astrometric registration in the
        difference image is also worse, leading to larger residuals in
        the lower-right panel.
        \label{fig:stages_bad}
    }
\end{figure*}

@@

Finally, for frames with the \texttt{DQUALITY} bit-flag corresponding
to the ``momentum dumps'' and ``coarse pointing modes'' described by
\citet{vanderspek_2018}, we omit the entire frame.  This removes on
average a few frames per sector, out of about one thousand. Through
visual inspection, we see that the stars on these frames are extremely
smeared, and are unlikely to produce useful science data.  In
addition, we use the sector-specific data release notes\footnote{\url{
  archive.stsci.edu/tess/tess_drn.html}} to identify further times
with anomalous spacecraft performance, which we omit from
consideration.  This included three days at the beginning of Sector 6
dedicated to acquiring pixel response function data. There were no
additional gaps in Sector 7.
%For Sectors 1 through 5, these
%include coarse pointing windows from orbits 10, 13, 14, and an
%instrumetal anomaly window in orbit 15.
% For Sectors 6 through 8, these include three days at the beginning of
% Sector 6 dedicated to acquiring pixel response function data, and also
% about three days during Sector 8 lost to an instrument anomaly.

@@

With the resulting WCS information, we then project a source catalog
onto each frame.  We use the projected positions of the sources to
center the apertures in our photometry, rather than attempting to
measure the positions.  Such ``forced-aperture photometry'' is
preferable to source extraction in the crowded fields that are central
to this work.  The Gaia-DR2 epoch is J2015.5, so even the
fastest-moving stars with proper motions of $\sim$$1\,{\rm
arcsecond}\,{\rm yr}^{-1}$ are still well within one pixel of their
predicted positions in the TESS images.  The projection from catalog
sky-coordinate positions to pixel coordinates is performed using an
analog of the \texttt{wcs-rd2xy} program that performs the standard
matrix algebra \citep{lang_2010}.  The source catalog look-up is
performed using
\texttt{gaia2read}\footnote{\url{github.com/samuelyeewl/gaia2read}}
\citep{kim_2018_gaia2read}.

@@

\begin{figure*}[!t]
	\gridline{
    \fig{detrended_light_curves_sec6cam1ccd4.pdf}{0.5\textwidth}{}
    \fig{detrended_light_curves_sec7cam3ccd2.pdf}{0.5\textwidth}{}
  }
	\vspace{-0.5cm}
	\caption{
    Twenty randomly selected light curves drawn from the same sector,
    camera, and CCD, for CDIPS target stars with $T$-band magnitudes
    between 13 and 14.  For each star, we show the raw light curve
    (top), PCA-detrended light curve (middle), and TFA-detrended light
    curve (bottom).  The sector, camera, and CCD numbers are 6, 1, 4
    (left) and 7, 3, 2 (right).  A number of systematic trends are
    shared across raw light curves ({\it e.g.}, the periodic $\sim$3 day
    ``chopping'' seen in the left plot).  In the PCA light curves,
    stellar rotation signals are usually preserved, but not always ({\it
    e.g.}, left panel, seventh from the top).  TFA filters out almost
    all long-term trends, or else heavily distorts them ({\it e.g.},
    right panel, fourth from the bottom)
	\label{fig:lc_systematics_dtr}
	}
\end{figure*}

@@

To determine the number of principal components at which to truncate
the model, we performed a cross-validation analysis.  Again, this was
achieved using \texttt{scikit-learn}.  As is typically the case when
the noise variance is different for each ``feature'' (each point in
time), we found that $k$-folding cross-validation of the PCA
components gave a cross-validation score that monotonically increased
with an increasing number of components\footnote{See for example
\url{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_vs_fa_model_selection.html}
(2019/08/06).}.  We found that if we instead performed a factor
analysis, the cross-validation score was typically maximized with
anywhere from $10$ to $15$ components.  This agreed with a visual
analysis of the number of PCA components past which overfitting began.
We therefore used the maximum cross-validation score from the factor
analysis as the number of principal components to use in each light
curve.  This number is documented in the \texttt{FITS} header of each
light curve.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{IRM-PCA-TFA_rms_vs_mag.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    Standard deviation of CDIPS light curves as a function of catalog
    TESS-band magnitude.  Left-to-right are raw, PCA-detrended, and
    TFA-detrended light curves. Black points correspond to the minimum
    RMS across the available three aperture sizes.  The model (orange
    and gray lines) assumes aperture sizes reported by
    \citet{Sullivan_et_al_2015}, and the effective area from
    \citet{vanderspek_2018}.  The noise from unresolved background
    stars (dotted gray line) is a function of galactic latitude, and
    dominates over zodiacal light for faint stars near the galactic
    plane; the line shown assumes a sight-line towards the center of
    Sector 6, Camera 1 (further details are in
    \S~\ref{subsubsec:rmsvsmag}).
		\label{fig:rms_vs_mag}
	}
\end{figure*}

@@

\acknowledgements
L.G.B.\ acknowledges helpful discussions with 
T.~Cantat-Gaudin,
C.~Huang,
M.~Soares-Furtado,
J.~Wallace, and
S.~Yee.  The authors are also
grateful to the many people who have turned TESS from an idea into
reality.
%
L.G.B. and J.H. acknowledge support by the TESS GI Program, program
G011103, through NASA grant 80NSSC19K0386.
%
G.B. acknowledges support through NASA grant NNG14FC03C.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This work made use of NASA's Astrophysics Data System Bibliographic
Services.
%
This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France. The original description of the VizieR service was
published in A\&AS 143, 23.
%
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral
Agreement.
%
The Digitized Sky Surveys were produced at the Space Telescope Science
Institute under U.S. Government grant NAG W-2166. The images of these
surveys are based on photographic data obtained using the Oschin
Schmidt Telescope on Palomar Mountain and the UK Schmidt Telescope.
The plates were processed into the present compressed digital form
with the permission of these institutions.
%
\newline
%
\facility{
	2MASS \citep{skrutskie_tmass_2006},
	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018},
	TESS \citep{ricker_transiting_2015},
	UCAC4 \citep{zacharias_fourth_2013}
    %DSS (CITE)    
}
%
\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{astroquery.gaia} CITE,
  %\texttt{astroquery.simbad} CITE,
  %\texttt{astroquery.mast} CITE,
  %\texttt{astroquery.nasaexopanetarchive} CITE,
  \texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{corner} \citep{corner_2016},
  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{fitsh} \citep{Pal_2012},
  \texttt{IPython} \citep{perez_2007},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122}
  \texttt{psycopg2} (\url{initd.org/psycopg})
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{scikit-learn} \citep{sklearn_2011},
  \texttt{TagSpaces} (\url{tagspaces.org}),
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
  \texttt{VARTOOLS} \citep{Hartman_Bakos_2016}
  \texttt{wotan} \citep{hippke_wotan_2019},
}

@@

In assigning a single unique cluster name to each star, we matched
against the \citet{Kharchenko_et_al_2013} name whenever possible,
since this was the largest available catalog, and it also included
homogeneous age determinations for many of the clusters.
To find the matching name, in order of precedence we
\begin{enumerate}
  \item Checked for direct string matches from
    \citet{Kharchenko_et_al_2013} clusters with determined parameters;
  \item Checked whether the SIMBAD online name resolving service \citep{wenger_simbad_2000} had
    any direct string matches against \citet{Kharchenko_et_al_2013}
    clusters with determined parameters;
  \item Checked for string matches in the full
    \citet{Kharchenko_et_al_2013} index (including clusters without
    determined parameters);
  \item Searched for spatial matches between each star and cluster
    centers from \citet{Kharchenko_et_al_2013} within 10 arcminutes.
    In cases with multiple cluster matches, we ignored candidate
    matches to avoid assigning incorrect names;
  \item Checked the WEBDA double name
    list\footnote{\url{https://webda.physics.muni.cz/double_names.html}},
    and repeated Steps 1-4 with any matches.
\end{enumerate}

>>>>

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{target_star_positions.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    Target star positions (blue) and nominal TESS observing footprint
    (gray).  Target stars are either candidate members of clusters, or
    else have other youth indicators (see \S~\ref{sec:starselection}).
    Most will be observed for one or two lunar months during the TESS
    Prime Mission.  Camera 1 is centered at $(l,b)=(203^\circ,
    -6^\circ)$ and $(218^\circ,15^\circ)$ in Sectors 6 and 7,
    respectively.
    \label{fig:cdips_targets_positions}
	}
\end{figure*}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\gridline{\fig{target_star_cumulative_counts.pdf}{0.43\textwidth}{}}
		\vspace{-0.8cm}
		\gridline{\fig{target_star_hist_logt.pdf}{0.43\textwidth}{}}
		\vspace{-0.8cm}
		\gridline{\fig{target_star_reference_pie_chart.pdf}{0.43\textwidth}{}}
	\end{center}
	\vspace{-0.8cm}
	\caption{
		Target star statistics.
		{\it Top.} Cumulative counts as a function of apparent Gaia $Rp$-band
		magnitude.  
		{\it Middle.} Histogram of target star ages, for the subset of
		stars with ages matched against \citet{Kharchenko_et_al_2013}.
		{\it Bottom.} Provenance of cluster membership.  Percentages are
		relative to $N_{\rm total}=1{,}061{,}446$ target stars. Symbols
		are as follows.
		D14 is \citet{dias_proper_2014}.
		K13 is \citet{Kharchenko_et_al_2013}.
		CG18 is \citet{cantat-gaudin_gaia_2018}.
		Z18 is \citet{zari_3d_2018}, with upper main sequence and
		pre-main-sequence samples sub-divided.
		``$\geq 2$'' indicates at least two authors reported a star as a
		candidate cluster member.
		%``Other'' refers to sources enumerated in \S~\ref{sec:starselection}.
		\label{fig:cdips_targets}
	}
\end{figure}

@@

\citet{Kharchenko_et_al_2013} used proper motions calculated in PPMXL
\citep[][a combination of USNO-B1{.}0 and 2MASS
astrometry]{roeser_ppmxl_2010} and near-infrared photometry from 2MASS
\citep{skrutskie_tmass_2006} to report the existence of 2859 open
clusters and stellar associations (globular clusters were omitted by
excluding any entry of type \texttt{'g'}).  We selected the most
probable cluster members (``$1\sigma$ members'') using the combined
photometric, kinematic, and spatial criteria described by
\citet[][Section~3.3]{kharchenko_global_2012}.  Then, to obtain {\it
Gaia}-DR2 source identifiers for the members, we performed a
crossmatch for Gaia-DR2 sources within 5 arcseconds of the listed
positions.  To improve the quality of the cross-match, we used the
2MASS photometry to predict the $G$-band magnitudes\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GDR2/Data_processing/chap_cu5pho/sec_cu5pho_calibr/ssec_cu5pho_PhotTransf.html},
(accessed \texttt{2019-03-29}), or \citet{carrasco_gaia_2016}}, and
required that the measured $G$-magnitude fall within 2 magnitudes of
the predicted $G$-magnitude.  If multiple neighbors matched the
position and magnitude constraints, we took the nearest spatial
neighbor as the match.  From 373{,}226 stars, this yielded a unique
best neighbor for 352{,}332 stars (94.4\% of the sample), and a choice
between two neighbors for 17{,}774 stars.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.35\textwidth]{pipelineoverview.pdf}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    Conceptual overview of photometric reduction pipeline.
    Details are given in \S~\ref{sec:method}.
	\label{fig:pipeline}
	}
\end{figure}

\begin{figure*}[!t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.93\textwidth]{stages_of_image_processing_good.png}
    \end{center}
    \vspace{-0.9cm}
    \caption{
        Stages of image processing for an image obtained during the middle
        of an orbit. Counts are in ADU.
        {\it Top right}. Calibrated image.
        {\it Top left}. Smooth background estimate.
        {\it Middle right}. Calibrated image minus its median pixel value.
        {\it Middle left}. Calibrated image minus smooth background.
        {\it Bottom left}. Difference image.
        {\it Bottom right}. Zoom of difference image, corresponding to
        the square with dashed lines.
        Each image is $(2048\times2048)$ pixels, except for the
        bottom-right image, which is $(512\times512)$.  All images
        except the top-right have identical color maps.  The sector,
        camera, and CCD are (6, 1, 2).
        \label{fig:stages_good}
    }
\end{figure*}

\begin{figure*}[!t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.93\textwidth]{stages_of_image_processing_bad.png}
    \end{center}
    \vspace{-0.7cm}
    \caption{
        Same sector, camera and CCD as Figure~\ref{fig:stages_good},
        but for an image obtained during perigee passage, when
        scattered light from the Earth is prominent.  A number of
        systematic artifacts are present, including vertical
        ``straps'' and small-scale structure in scattered light
        patches.  The quality of astrometric registration in the
        difference image is also worse, leading to larger residuals in
        the lower-right panel.
        \label{fig:stages_bad}
    }
\end{figure*}

@@

Finally, for frames with the \texttt{DQUALITY} bit-flag corresponding
to the ``momentum dumps'' and ``coarse pointing modes'' described by
\citet{vanderspek_2018}, we omit the entire frame.  This removes on
average a few frames per sector, out of about one thousand. Through
visual inspection, we see that the stars on these frames are extremely
smeared, and are unlikely to produce useful science data.  In
addition, we use the sector-specific data release notes\footnote{\url{
  archive.stsci.edu/tess/tess_drn.html}, accessed \texttt{2019-08-12}} to identify further times
with anomalous spacecraft performance, which we omit from
consideration.  This included three days at the beginning of Sector 6
dedicated to acquiring pixel response function data. There were no
additional gaps in Sector 7.

@@

With the resulting WCS information, we then project a source catalog
onto each frame.  We use the projected positions of the sources to
center the apertures in our photometry, rather than attempting to
measure the positions.  Such ``forced-aperture photometry'' is
preferable to source extraction in the crowded fields that are central
to this work.  The Gaia-DR2 epoch is J2015.5, so even the
fastest-moving stars with proper motions of $\sim$$1\,{\rm
arcsecond}\,{\rm yr}^{-1}$ are still well within one pixel of their
predicted positions in the TESS images.  The projection from catalog
sky-coordinate positions to pixel coordinates is performed using an
analog of the \texttt{wcs-rd2xy} program that performs the standard
matrix algebra \citep{lang_2010}.  The source catalog look-up is
performed using
\texttt{gaia2read}\footnote{\url{github.com/samuelyeewl/gaia2read}, commit \texttt{4b472d}}
\citep{kim_2018_gaia2read}.

@@

\begin{figure*}[!t]
	\gridline{
    \fig{detrended_light_curves_sec6cam1ccd4.pdf}{0.5\textwidth}{}
    \fig{detrended_light_curves_sec7cam3ccd2.pdf}{0.5\textwidth}{}
  }
	\vspace{-0.85cm}
	\caption{
    Twenty randomly selected light curves drawn from the same sector,
    camera, and CCD, for CDIPS target stars with $T$-band magnitudes
    between 13 and 14.  For each star, we show the raw light curve
    (top), PCA-detrended light curve (middle), and TFA-detrended light
    curve (bottom).  The sector, camera, and CCD numbers are 6, 1, 4
    (left) and 7, 3, 2 (right).  A number of systematic trends are
    shared across raw light curves ({\it e.g.}, the periodic $\sim$3 day
    ``chopping'' seen in the left plot).  In the PCA light curves,
    stellar rotation signals are usually preserved, but not always ({\it
    e.g.}, left panel, seventh from the top).  TFA filters out almost
    all long-term trends, or else heavily distorts them ({\it e.g.},
    right panel, fourth from the bottom)
	\label{fig:lc_systematics_dtr}
	}
\end{figure*}

@@

To determine the number of principal components at which to truncate
the model, we performed a cross-validation analysis.  Again, this was
achieved using \texttt{scikit-learn}.  As is typically the case when
the noise variance is different for each ``feature'' (each point in
time), we found that $k$-folding cross-validation of the PCA
components gave a cross-validation score that monotonically increased
with an increasing number of components\footnote{See for example
\url{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_vs_fa_model_selection.html}, accessed \texttt{2019-08-06}.}.  We found that if we instead performed a factor
analysis, the cross-validation score was typically maximized with
anywhere from $10$ to $15$ components.  This agreed with a visual
analysis of the number of PCA components past which overfitting began.
We therefore used the maximum cross-validation score from the factor
analysis as the number of principal components to use in each light
curve.  This number is documented in the \texttt{FITS} header of each
light curve.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{IRM-PCA-TFA_rms_vs_mag.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    Standard deviation of CDIPS light curves as a function of catalog
    TESS-band magnitude.  Left-to-right are raw, PCA-detrended, and
    TFA-detrended light curves. Black points correspond to the minimum
    RMS across the available three aperture sizes.  The model (orange
    and gray lines) assumes aperture sizes reported by
    \citet{Sullivan_et_al_2015}, and the effective area from
    \citet{vanderspek_2018}.  The noise from unresolved background
    stars (dotted gray line) is a function of galactic latitude, and
    dominates over zodiacal light for faint stars near the galactic
    plane; the line shown assumes a sight-line towards the center of
    Sector 6, Camera 1 (further details are in
    \S~\ref{subsubsec:rmsvsmag}).
		\label{fig:rms_vs_mag}
	}
\end{figure*}

@@

\acknowledgements
L.G.B.\ acknowledges helpful discussions with 
T.~Cantat-Gaudin,
C.~Huang,
M.~Soares-Furtado,
J.~Wallace, and
S.~Yee.  The authors are also
grateful to the many people who have turned TESS from an idea into
reality.
%
L.G.B. and J.H. acknowledge support by the TESS GI Program, program
G011103, through NASA grant 80NSSC19K0386.
%
G.B. acknowledges support through NASA grant NNG14FC03C.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This work made use of NASA's Astrophysics Data System Bibliographic
Services.
%
This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France. The original description of the VizieR service was
published in A\&AS 143, 23.
%
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral
Agreement.
%
The Digitized Sky Surveys were produced at the Space Telescope Science
Institute under U.S. Government grant NAG W-2166. The images of these
surveys are based on photographic data obtained using the Oschin
Schmidt Telescope on Palomar Mountain and the UK Schmidt Telescope.
%
\newline
%
\facility{
	2MASS \citep{skrutskie_tmass_2006},
	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018},
	TESS \citep{ricker_transiting_2015},
	UCAC4 \citep{zacharias_fourth_2013}
    %DSS (CITE)    
}
%
\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{astroquery.gaia} CITE,
  %\texttt{astroquery.simbad} CITE,
  %\texttt{astroquery.mast} CITE,
  %\texttt{astroquery.nasaexopanetarchive} CITE,
  \texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{corner} \citep{corner_2016},
  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{fitsh} \citep{Pal_2012},
  \texttt{IPython} \citep{perez_2007},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122}
  \texttt{psycopg2} (\url{initd.org/psycopg})
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{scikit-learn} \citep{sklearn_2011},
  \texttt{TagSpaces} (\url{tagspaces.org}),
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
  \texttt{VARTOOLS} \citep{Hartman_Bakos_2016}
  \texttt{wotan} \citep{hippke_wotan_2019},
}

@@

In assigning a single unique cluster name to each star, we matched
against the \citet{Kharchenko_et_al_2013} name whenever possible,
since this was the largest available catalog, and it also included
homogeneous age determinations for many of the clusters.
To find the matching name, in order of precedence we
\begin{enumerate}
  \item Checked for direct string matches from
    \citet{Kharchenko_et_al_2013} clusters with determined parameters;
  \item Checked whether the SIMBAD online name resolving service \citep{wenger_simbad_2000} had
    any direct string matches against \citet{Kharchenko_et_al_2013}
    clusters with determined parameters;
  \item Checked for string matches in the full
    \citet{Kharchenko_et_al_2013} index (including clusters without
    determined parameters);
  \item Searched for spatial matches between each star and cluster
    centers from \citet{Kharchenko_et_al_2013} within 10 arcminutes.
    In cases with multiple cluster matches, we ignored candidate
    matches to avoid assigning incorrect names;
  \item Checked the WEBDA double name
    list\footnote{\url{https://webda.physics.muni.cz/double_names.html}, accessed \texttt{2019-08-12}},
    and repeated Steps 1-4 with any matches.
\end{enumerate}
